Guarded Recursion in Agda via Sized Types

### 2019-01-11 code-oneclock-paper/latex/paper.tex
First draft of section 4
Added bibliography
WIP: beginning of introduction

\title{Guarded Recursive Type Theory via Sized Types}

@@

\section{Introduction}
\label{sec:intro}
\cite{atkey2013productive}

@@

%\input{CloTT/Structure/ContextOperations} Context operations and simple type forrmers are not interesting. There is not much to tell about them, so a remark suffices.

>>>>

\title{Guarded Recursion in Agda via Sized Types}

@@

\section{Introduction}
\label{sec:intro}
\input{Introduction}
\nocite{*}

@@

\input{CloTT/Structure/ContextOperations}

Lastly, we use operations on sets and presheaves to define the type operators in simple type theory.
For sets, we use products, sums, and function types in Agda.
Products, sums, and exponentials of presheaves are interpreted with the operations in \Cref{sec:presheaves}.
